Fractional Types

### 2016-12-19 typespp.tex
Fix packl/packr typesetting

The adaptation of the combinators to the pointed dependent setting in Fig .~\ref
{pifracd:comb} is relatively straightforward. First, the types of the
combinators must keep track of how the value currently in focus changes during
evaluation, and hence directly encode the operational semantics of the
language. As suggested above, the quantifiers are interpreted differently
depending on which direction the rule is used. We use a $\forall\exists$
notation to express the presence of \emph{one} quantifier that is interpreted
differently in each direction. The notation has the advantage of being compact,
avoiding duplication, and making the symmetry of the rules explicit. We also
include two new pairs of combinators $\synchl/packl$ and $\synchr/packr$ that
serve as explicit quantifier introduction and elimination rules: they serve as
explicit ``synchronization'' points as illustrated in the example below.

@@

>>>>

The adaptation of the combinators to the pointed dependent setting in Fig .~\ref
{pifracd:comb} is relatively straightforward. First, the types of the
combinators must keep track of how the value currently in focus changes during
evaluation, and hence directly encode the operational semantics of the
language. As suggested above, the quantifiers are interpreted differently
depending on which direction the rule is used. We use a $\forall\exists$
notation to express the presence of \emph{one} quantifier that is interpreted
differently in each direction. The notation has the advantage of being compact,
avoiding duplication, and making the symmetry of the rules explicit. We also
include two new pairs of combinators $\synchl/\packl$ and $\synchr/\packr$ that
serve as explicit quantifier introduction and elimination rules: they serve as
explicit ``synchronization'' points as illustrated in the example below.

@@

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
    \path (-1,2) edge node[above] {\footnotesize{${\textsf{\#c}}$}} (2,2);
    \path (-1,0.5) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (0,0.5);

    \draw (0,-0.25) -- (1,-0.25) -- (1,1.5) -- (0,1.5) -- cycle;
    \node at (0.5,0.6) {\footnotesize{$\textsf{name}_p$}};

    \path (1,1.25) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (2,1.25);
    \path (1,0) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (4,0);

    \draw (2,1) -- (3,1) -- (3,2.25) -- (2,2.25) -- cycle;
    \node at (2.5,1.625) {\footnotesize{$\epsilon +$}};

    \path (3,1.625) edge node[above] {\footnotesize{$\textsf{\#id}$}} (4,1.625);

    \draw (4,-0.25) -- (5,-0.25) -- (5,2) -- (4,2) -- cycle;
    \node at (4.5,0.85) {\footnotesize{$\unititl/$}};

    \path (5,0.85) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,0.85);
  \end{tikzpicture}
  \caption{\label{fig:apply} apply}
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
    \path (-1,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (0,1);

    \path (1,1.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,1.75);
    \path (1,0.25) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,0.25);

    \draw (2,1.25) -- (3,1.25) -- (3,2.25) -- (2,2.25) -- cycle;
    \node at (2.5,1.75) {\footnotesize{$\textsf{name}_{p_1}$}};

    \path (3,2.125) edge node[above] {\footnotesize{${1/\textsf{\#c}}$}} (8,2.125);
    \path (3,1.375) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (4,1.375);

    \draw (2,0.75) -- (3,0.75) -- (3,-0.25) -- (2,-0.25) -- cycle;
    \node at (2.5,0.25) {\footnotesize{$\textsf{name}_{p_2}$}};

    \path (3,0.625) edge node[above] {\footnotesize{${1/\textsf{\#d}}$}} (4,0.625);
    \path (3,-0.125) edge node[above] {\footnotesize{${\textsf{\#e}}$}} (6,-0.125);

    \draw (4,1.5) -- (5,1.5) -- (5,0.5) -- (4,0.5) -- cycle;
    \node at (4.5,1) {\footnotesize{$\epsilon +$}};

    \path (5,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (6,1);

    \draw (6,1.125) -- (7,1.125) -- (7,-0.25) -- (6,-0.25) -- cycle;
    \node at (6.5,0.5) {\footnotesize{$\unititl/$}};

    \path (7,0.5) edge node[above] {\footnotesize{${\textsf{\#e}}$}} (8,0.5);
  \end{tikzpicture}
  \caption{\label{fig:compose} compose}
\end{figure}
